---
title: "Housing - Rent Datasets, Curitiba"
author: "Lucas Salamuni"
date: "2024-03-08"
output:
  html_document:
    df_print: paged
---



# 1. PACKAGES


## 1.1. Downloading packages
```{r echo=TRUE, message=FALSE, warning=FALSE}

pacotes <- c("dplyr", "tidyverse", "rvest", "readr", "stringr", "curl", "tidyr",
             "magrittr", "RSelenium", "netstat", "wdman", "openxlsx", "readxl") 

if(sum(as.numeric(!pacotes %in% installed.packages())) != 0){ 
  instalador <- pacotes[!pacotes %in% installed.packages()] 
  for(i in 1:length(instalador)) {
    install.packages(instalador, dependencies = T)
    break()}
  sapply(pacotes, require, character = T)
} else {
  sapply(pacotes, require, character = T)
}

```

---

# 2. DATA SCRAPING I AND PRELIMINAR WRANGLING - QUINTO ANDAR


## 2.1. Data wrangling function I
```{r echo=TRUE}

extract_rental_info <- function() {
  page_source <- remDr$getPageSource()[[1]] %>% read_html()
  df <- page_source %>%
    html_nodes("h2") %>%
    html_text() %>%
  tibble() %>%
  slice_head(n = -2) %>%
  rename(geral = 1) %>%
  mutate(geral = paste0(geral, " ·")) %>%
  group_by(observation_id = ceiling(row_number()/2)) %>%
  summarise(geral = paste(geral, collapse = " ")) %>%
  select(-observation_id) %>%
  separate(geral, into = c("Type", "Address", "City"), 
           sep = " ·", extra = "merge") %>%
  mutate(City = str_replace(City, " ·", "")) %>%
  separate(Address, into = c("Street", "Neighborhood"), 
           sep = ", ", remove = TRUE) %>%
  bind_cols(
    remDr$getPageSource()[[1]] %>%
      read_html() %>%
      html_nodes("h3") %>%
      html_text() %>%
      tibble() %>%
      slice_head(n = -4) %>%
      rename(geral = 1) %>%
      mutate(geral = paste0(geral, " ·")) %>%
      group_by(observation_id = ceiling(row_number()/3)) %>%
      summarise(geral = paste(geral, collapse = " ")) %>%
      select(-observation_id) %>%
      separate(geral, into = c("Total", "Rent", "Area_sqm",
                               "N_rooms", "N_parking_spaces"), 
               sep = " ·", extra = "merge") %>%
      mutate(N_parking_spaces = str_replace(N_parking_spaces, " ·", "")) %>%
      mutate(N_parking_spaces = str_replace_all(N_parking_spaces, " vaga(s)?", "")) %>%
      mutate(N_rooms = str_replace_all(N_rooms, " quarto(s)?", "")) %>%
      mutate(Area_sqm = str_replace_all(Area_sqm, "m²", "")) %>%
      mutate(Rent = str_remove_all(str_remove_all(Rent, "R\\$"), "\\.")) %>%
      mutate(Rent = str_remove_all(Rent, "aluguel")) %>%
      mutate(Rent = str_trim(Rent, side = "left")) %>%
      mutate(Total = str_remove_all(str_remove_all(Total, "R\\$"), "\\.")) %>%
      mutate(Total = str_trim(Total, side = "left")) %>%
      mutate(Total = str_remove_all(Total, "total")) %>%
      mutate_at(vars(Total, Rent, Area_sqm, 
                     N_rooms, N_parking_spaces), as.numeric) %>%
      mutate(N_parking_spaces = replace_na(N_parking_spaces, 0))
  ) %>%
  relocate(Area_sqm, .after = "Type") %>%
  relocate(N_rooms, .after = "Area_sqm") %>%
  relocate(N_parking_spaces, .after = "N_rooms") %>%
  relocate(Rent, .before = "Total")

  return(df)
}

```


## 2.2. Setting up RSelenium
```{r eval=FALSE}

selenium()

selenium_object <- selenium(retcommand = TRUE,
                            check = FALSE)
selenium_object

```


## 2.3. Starting the server
```{r eval=FALSE}

rs_driver_object <- rsDriver(browser = "chrome",
                             chromever = "129.0.6668.58",
                             verbose = FALSE,
                             port = free_port())

```


## 2.4. Scraping = QuintoAndar
```{r eval=FALSE}

iterations <- 74

remDr <- rs_driver_object$client
remDr$open()
remDr$maxWindowSize()
remDr$setTimeout(type = "script", milliseconds = 1 * 60 * 60 * 1000)
remDr$navigate("https://www.quintoandar.com.br/alugar/imovel/curitiba-pr-brasil")

page_source_cwb <- NULL
for (i in 1:iterations) {
  Sys.sleep(1)
  css_selector <- sprintf("div.MuiBox-root:nth-child(%d) > button:nth-child(1)", (i-1)*4 + 6)
  remDr$executeScript(sprintf("document.querySelector('%s').scrollIntoView();", css_selector))
  Sys.sleep(1)
  ver_mais_button <- remDr$findElement(using = "css selector", value = css_selector)
  Sys.sleep(1)
  ver_mais_button$clickElement()
  Sys.sleep(3)
  page_source_cwb <- c(page_source_cwb)
}

df_cwb <- extract_rental_info()

remDr$close()

```
* NOTE: One of my challenges in developing a scraping function for Quinto Andar was the fact that, apparently, the HTML structure of the website changes constantly. Therefore, I had to create the function for this site twice. Hence, it wouldn't be surprising if the function in this script is obsolete. However, I didn't confirm this, as I didn't run this chunk after collecting the data I needed.


```{r include=FALSE}

df_cwb <- read_excel("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Housing/CWB_Dataset_I-NW.xlsx")

```

---

# 3. FURTHER DATA WRANGLING I - QUINTO ANDAR


## 3.1. Checking for NAs
```{r echo=TRUE}
results <- vector("list", length = ncol(df_cwb))

for (i in seq_along(names(df_cwb))) {
  results[[i]] <- df_cwb %>%
    summarise(NAs = sum(is.na(!!sym(names(df_cwb)[i]))))
}

results_df <- bind_rows(results, .id = "Column")

print(results_df)

```


## 3.2. Removing empty spaces from the text columns
```{r echo=TRUE}

df_na <- df_cwb

df_na <- df_na %>%
  mutate_at(vars(Type, Street, Neighborhood, City), ~str_trim(as.character(.)))

```


## 3.3. Removing parenthesis and other special characters 
```{r echo=TRUE}

df_na <- df_na %>%
  mutate(Neighborhood = str_replace_all(Neighborhood, "\\(.*?\\)", ""))

```


## 3.4. Checking for duplicated entries
```{r echo=TRUE}

duplicates <- df_na[duplicated(df_na[, c("Type", "Area_sqm", "N_rooms", 
                                         "N_bathrooms", "N_parking_spaces", "Street", 
                                         "Neighborhood", "City", "Rent", "Total")]) 
                    | duplicated(df_na[, c("Type", "Area_sqm", "N_rooms", "N_bathrooms", 
                                           "N_parking_spaces", "Street", "Neighborhood", 
                                           "City", "Rent", "Total")], fromLast = TRUE), ]

duplicates %>%
  arrange(Street) %>%
  head(10)

```


## 3.5. Removing duplicates from the dataset
```{r echo=TRUE}

df_na <- unique(df_na[, c("Type", "Area_sqm", "N_rooms", "N_bathrooms", "N_parking_spaces", 
                          "Street", "Neighborhood", "City", "Rent", "Total")])

duplicates <- df_na[duplicated(df_na[, c("Type", "Area_sqm", "N_rooms", "N_bathrooms", 
                                         "N_parking_spaces", "Street", "Neighborhood", 
                                         "City", "Rent", "Total")]) 
                    | duplicated(df_na[, c("Type", "Area_sqm", "N_rooms", "N_bathrooms", 
                                           "N_parking_spaces", "Street", "Neighborhood", 
                                           "City", "Rent", "Total")], fromLast = TRUE), ]

duplicates %>%
  arrange(Street) %>%
  head(10)

```


## 3.6. Standardizing the Type column
```{r echo=TRUE}

unique(df_na$Type)

df_na <- df_na %>%
  mutate(Type = case_when(
    Type %in% c("Apartamento", "Studio e kitnet", "Casa em condomínio") ~ "Condominio",
      TRUE ~ Type
  ))

unique(df_na$Type)

```


## 3.7. Checking for outliers in 'Area_sqm' column
```{r echo=TRUE}

df_na %>%
  arrange(Area_sqm) %>%
  head(10)

df_na %>%
  arrange(desc(Area_sqm)) %>%
  head(10)

```


## 3.8. Removing the 'Street' and 'Rent' columnns, and renaming 'Total' to 'Rent'
```{r echo=TRUE}

df_na <- df_na %>%
  select(-c(Street, Rent)) %>%
  rename(Rent = Total)

```


## 3.9. Checking for outliers in 'Neighborhood' column
```{r echo=TRUE}

df_na %>%
  arrange(Neighborhood) %>%
  head(10)

df_na %>%
  arrange(desc(Neighborhood)) %>%
  head(10)

df_na <- df_na %>%
  mutate(Neighborhood = iconv(Neighborhood, "UTF-8", "ASCII//TRANSLIT"))

df_na %>%
  arrange(Neighborhood) %>%
  head(10)

df_na %>%
  arrange(desc(Neighborhood)) %>%
  head(10)

```


## 3.10. Saving the dataframe as an xlsx file
```{r eval=FALSE}

df_cwb <- df_na

file <- "CWB_Dataset_I.xlsx"
folder <- paste0("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Housing/", file)
write.xlsx(df_cwb, folder, rowNames = FALSE)

```

---

# 4. DATA SCRAPING II AND PRELIMINAR WRANGLING - IMÓVEL WEB


## 4.1. Data wrangling function II
```{r echo=TRUE}

extract_rental_info_ii <- function() {
  page_source <- remDr$getPageSource()[[1]] %>% read_html()
  df <- page_source %>%
    html_nodes("h3") %>%
    html_text() %>%
    tibble() %>%
    rename(geral = 1) %>%
    mutate(geral = paste0(geral, " ·")) %>%
    group_by(observation_id = ceiling(row_number()/2)) %>%
    summarise(geral = paste(geral, collapse = " ")) %>%
    select(-observation_id) %>%
    separate(geral, into = c("Infos", "Description"), sep = " ·", extra = "merge") %>%
    separate(Infos, into = c("Area_sqm", "Infos"), sep = "tot.", extra = "merge") %>%
    mutate(Area_sqm = str_replace_all(Area_sqm, "m²", "")) %>%
    mutate(Infos = ifelse(!str_detect(Infos, "quartos"), 
                          paste0("1 quartos", Infos), Infos)) %>%
    separate(Infos, into = c("N_rooms", "Infos"), sep = "quartos", extra = "merge") %>%
    separate(Infos, into = c("N_bathrooms", "N_parking_spaces"), sep = "ban.", 
             extra = "merge") %>%
    mutate(N_parking_spaces = str_replace(N_parking_spaces, "eiro", "")) %>%
    mutate(N_parking_spaces = str_replace(N_parking_spaces, "vaga", "")) %>%
    mutate_at(vars(Area_sqm, N_rooms, N_bathrooms, N_parking_spaces), as.numeric) %>%
    mutate(N_parking_spaces = replace_na(N_parking_spaces, 0)) %>%
    select(-Description) %>%
    bind_cols(
      page_source %>%
        html_nodes("h2") %>%
        html_text() %>%
        tibble(geral = .) %>%
        separate(geral, into = c("Neighborhood", "City"), sep = ", ", extra = "merge") %>%
        mutate_at(vars(Neighborhood, City), ~str_trim(as.character(.)))
    ) %>%
    bind_cols({
      div_data <- page_source %>%
        html_nodes("div") %>%
        html_text() %>%
        tibble(geral = .) %>%
        filter_all(any_vars(!is.na(.) & str_detect(., "\\S"))) %>%
        filter(str_detect(geral, "^\\s*R\\$")) %>%
        filter(str_length(geral) > 50) %>%
        distinct() %>%
        filter(!str_detect(geral, "Super destaque")) %>%
        filter(!str_detect(geral, "WhatsAppContatar")) %>% 
        filter(!str_detect(geral, "Contatar")) %>%
        mutate(Rent = str_extract(geral, "(?<=R\\$)[^R]+")) %>%
        mutate(Rent = ifelse(str_detect(Rent, "\\d{2}%"),
                             str_replace(Rent, "\\d{2}%", ""), Rent)) %>%
        mutate(Rent = str_replace_all(Rent, "\\.", "")) %>%
        mutate(geral = str_replace_all(geral, "R\\$[^R]+R\\$", "")) %>%
        mutate(geral = str_replace_all(geral, "[0-9.\\s]+", "")) %>%
        mutate(Type = str_extract(geral, "[A-Z][^A-Z]*")) %>%
        mutate(geral = str_remove(geral, "[A-Z][^A-Z]*")) %>%
        separate(geral, into = c("Address", "geral"),
                 sep = ",", extra = "merge") %>%
        mutate(Type = ifelse(Type == "R$", "Casa", Type)) %>%
        mutate(Type = ifelse(Type == "R$%", "Casa", Type)) %>%
        mutate(geral = str_remove(geral, "Curitiba.*")) %>%
        select(-geral) %>%
        mutate(Address = str_replace_all(Address, "([A-Z])", " \\1"))
      if (nrow(div_data) == 19) {
        additional_row <- tibble(Address = NA, Rent = NA, Type = NA)
        div_data <- bind_rows(div_data, additional_row)
      }
      div_data
    }) %>%
    mutate(Address = str_replace_all(Address, paste(Neighborhood, collapse = "|"), "")) %>%
    mutate(N_bathrooms = ifelse(is.na(N_bathrooms), 1, N_bathrooms)) %>%
    mutate(Rent = str_extract(Rent, "\\d+")) %>%
    mutate_at(vars(Rent), as.numeric) %>%
    filter(!is.na(Area_sqm)) %>%
    rename(Street = Address) %>%
    filter(!is.na(Type) | !is.na(Street) | !is.na(Rent)) %>%
    mutate_at(vars(Street), ~str_trim(as.character(.))) %>%
    relocate(Type, .before = "Area_sqm") %>%
    relocate(Street, .after = "N_parking_spaces")
  return(df)
}

```


## 4.2. Scraping = ImovelWeb
```{r eval=FALSE}

iterations <- 149 

page_source_cwb <- list()
for (page_number in 1:iterations) {
  remDr <- rs_driver_object$client
  url <- paste0("https://www.imovelweb.com.br/casas-apartamentos-aluguel-curitiba-pr-pagina-", 
                page_number, ".html")
  remDr$open()
  remDr$navigate(url)
  df <- extract_rental_info_ii()
  page_source_cwb[[page_number]] <- df
  remDr$close()
}

df_cwb_ii <- do.call(rbind, page_source_cwb)

```

---

```{r include=FALSE}

df_cwb_ii <- read_excel("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Housing/CWB_Dataset_II-NW.xlsx")

```

# 5. FURTHER DATA WRANGLING II - IMOVEL WEB


## 5.1. Checking for outliers in 'Type' column
```{r echo=TRUE}

df_na <- df_cwb_ii

unique(df_na$Type)

df_na <- df_na %>%
  mutate(Type = if_else(str_detect(Type, "(?i)Condominio"), "Condominio", "Casa"))

unique(df_na$Type)

df_na <- df_na %>%
  mutate(Type = if_else(is.na(Type) | str_detect(Type, "(?i)Condominio"), "Condominio", "Casa"))

unique(df_na$Type)

```


## 5.2. Checking for duplicated entries
```{r echo=TRUE}

duplicates <- df_na[duplicated(df_na[, c("Type", "Area_sqm", "N_rooms", "N_bathrooms", 
                                         "N_parking_spaces", "Neighborhood", "City", 
                                         "Rent")]) 
                    | duplicated(df_na[, c("Type", "Area_sqm", "N_rooms", "N_bathrooms", 
                                           "N_parking_spaces", "Neighborhood", "City", 
                                           "Rent")], fromLast = TRUE), ]

duplicates %>%
  arrange(Type) %>%
  head(10)

```


## 5.3. Removing duplicates from the dataset
```{r echo=TRUE}

df_na <- unique(df_na[, c("Type", "Area_sqm", "N_rooms", "N_bathrooms", "N_parking_spaces", 
                          "Neighborhood", "City", "Rent")])

duplicates <- df_na[duplicated(df_na[, c("Type", "Area_sqm", "N_rooms", "N_bathrooms", 
                                         "N_parking_spaces", "Neighborhood", "City", "Rent")]) 
                    | duplicated(df_na[, c("Type", "Area_sqm", "N_rooms", "N_bathrooms", 
                                           "N_parking_spaces", "Neighborhood", "City", 
                                           "Rent")], fromLast = TRUE), ]

duplicates %>%
  arrange(Type) %>%
  head(10)

```


## 5.4. Checking for outliers in 'Area_sqm' column
```{r echo=TRUE}

df_na %>%
  arrange(Area_sqm) %>%
  head(10)

df_na %>%
  arrange(desc(Area_sqm)) %>%
  head(50)

df_na <- df_na %>%
  filter(Area_sqm >= 10 & Area_sqm <= 1000)

df_na %>%
  arrange(Area_sqm) %>%
  head(10)

df_na %>%
  arrange(desc(Area_sqm)) %>%
  head(50)

```


## 5.5. Checking for outliers in 'Neighborhood' column
```{r echo=TRUE}

df_na %>%
  arrange(Neighborhood) %>%
  head(10)

df_na %>%
  arrange(desc(Neighborhood)) %>%
  head(10)

df_na <- df_na %>%
  mutate(Neighborhood = iconv(Neighborhood, "UTF-8", "ASCII//TRANSLIT"))

df_na %>%
  arrange(desc(Neighborhood)) %>%
  head(10)

```


## 5.6. Saving the dataframe as an xlsx file
```{r eval=FALSE}

df_cwb_ii <- df_na

file <- "CWB_Dataset_II.xlsx"
folder <- paste0("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Housing/", file)
write.xlsx(df_cwb_ii, folder, rowNames = FALSE)

```

---

# 6. DATA SCRAPING III AND PRELIMINAR WRANGLING - VIVA REAL


## 6.1. Data wrangling function III
```{r echo=TRUE}

extract_rental_info_iii <- function() {
  page_source <- remDr$getPageSource()[[1]] %>% read_html()
  df <- page_source %>%
    html_nodes("h2") %>%
    html_text() %>%
    tibble(geral = .) %>%
    slice_head(n = 36) %>%
    mutate(geral = str_squish(geral)) %>%
    mutate(Type = word(geral, 1, 1),
           geral = str_remove(geral, "^\\S+\\s")) %>%
    mutate(geral = str_remove(geral, "^[^,]+,\\s*")) %>%
    mutate(Area_sqm = as.numeric(str_extract(geral, "\\d+")),
           geral = str_remove(geral, "\\d+")) %>%
    mutate(geral = str_remove(geral, "m²")) %>%
    mutate(Street = str_extract(geral, "^[^-]+"),
           geral = str_remove(geral, "^[^-]+"),
           geral = str_remove(geral, "- "),
           geral = str_remove(geral, "- PR ver mapa")) %>%
    mutate(Neighborhood = str_extract(geral, "^[^,]+"),
           City = str_remove(geral, "^[^,]+,\\s*")) %>%
    mutate(Street = str_trim(Street),
           Neighborhood = str_trim(Neighborhood),
           City = str_trim(City)) %>%
    mutate(Neighborhood = if_else(City != "Curitiba", 
                                  str_extract(Street, "^[^,]+"), Neighborhood),
           City = if_else(City != "Curitiba", 
                          str_extract(Street, "[^,]+$"), City),
           Street = if_else(City != "Curitiba", NA_character_, Street)) %>%
    mutate(Neighborhood = iconv(Neighborhood, "UTF-8", "ASCII//TRANSLIT")) %>%
    mutate(Street = str_trim(Street),
           Neighborhood = str_trim(Neighborhood),
           City = str_trim(City)) %>%
    select(-geral) %>%
    bind_cols(
      page_source %>%
        html_nodes("p") %>%
        html_text() %>%
        tibble(Rent = .) %>%
        slice_head(n = 36) %>%
        mutate(Rent = str_squish(Rent)) %>%
        mutate(Rent = str_remove_all(Rent, "\\.")) %>%
        mutate(Rent = as.numeric(str_extract(Rent, "\\d+")))
    ) %>%
    bind_cols(
      page_source %>%
        html_nodes("li") %>%
        html_text() %>%
        tibble(geral = .) %>%
        filter(!str_detect(geral, "m²")) %>%
        mutate(geral = str_squish(geral)) %>%
        filter(str_detect(geral, "Quarto|Quartos|Banheiro|Banheiros|Vaga|Vagas")) %>%
        group_by(observation_id = ceiling(row_number()/3)) %>%
        summarise(geral = paste(geral, collapse = " ")) %>%
        slice(1:36) %>%
        select(geral) %>%
        mutate(N_rooms = str_extract(geral, "(\\d+) Quarto(s)?"),
               geral = str_remove(geral, "(\\d+) Quarto(s)?")) %>%
        mutate(N_bathrooms = str_extract(geral, "(\\d+) Banheiro(s)?"),
               N_parking_spaces = str_remove(geral, "(\\d+) Banheiro(s)?")) %>%
        select(-geral) %>%
        mutate(N_parking_spaces = str_replace(N_parking_spaces, "--", "0")) %>%
        mutate_at(vars(N_rooms, N_bathrooms, N_parking_spaces), 
                  ~as.numeric(gsub("[^0-9.]", "", .)))
    ) %>%
    relocate(Street, .after = "N_parking_spaces") %>%
    relocate(Neighborhood, .after = "Street") %>%
    relocate(City, .after = "Neighborhood") %>%
    relocate(Rent, .after = "City")
  return(df)
}

```


## 6.2. Scraping = VivaReal
```{r eval=FALSE}

iterations <- 96 #OBS³

page_source_cwb <- list()
for (page_number in 1:iterations) {
  remDr <- rs_driver_object$client
  url <- paste0("https://www.vivareal.com.br/aluguel/parana/curitiba/?pagina=", 
                page_number, "#onde=Brasil,Paran%C3%A1,Curitiba,,,,,,BR%3EParana%3ENULL%3ECuritiba,,,&tipos=apartamento_residencial,casa_residencial,condominio_residencial,cobertura_residencial,flat_residencial,kitnet_residencial,sobrado_residencial,edificio-residencial_comercial")
  remDr$open()
  remDr$navigate(url)
  Sys.sleep(5)
  df <- extract_rental_info_iii()
  page_source_cwb[[page_number]] <- df
  remDr$close()
}

df_cwb_iii <- do.call(rbind, page_source_cwb)

```

---

```{r include=FALSE}

df_cwb_iii <- read_excel("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Housing/CWB_Dataset_III-NW.xlsx")

```

# 7. FURTHER DATA WRANGLING III - VIVA REAL


## 7.1. Checking for NAs
```{r echo=TRUE}

results <- vector("list", length = ncol(df_cwb_iii))

for (i in seq_along(names(df_cwb_iii))) {
  results[[i]] <- df_cwb_iii %>%
    summarise(NAs = sum(is.na(!!sym(names(df_cwb_iii)[i]))))
}

results_df <- bind_rows(results, .id = "Column")

print(results_df)

```


## 7.2. Removing NAs from the text columns
```{r echo=TRUE}

df_na <- df_cwb_iii

df_na <- df_na %>%
  filter(!is.na(Area_sqm)) %>%
  filter(!is.na(N_rooms))

results <- vector("list", length = ncol(df_na))

for (i in seq_along(names(df_cwb_iii))) {
  results[[i]] <- df_na %>%
    summarise(NAs = sum(is.na(!!sym(names(df_na)[i]))))
}

results_df <- bind_rows(results, .id = "Column")

print(results_df)

```


## 7.3. Checking for duplicated entries
```{r echo=TRUE}

duplicates <- df_na[duplicated(df_na[, c("Type", "Area_sqm", "N_rooms", "N_parking_spaces", 
                                         "Street", "Neighborhood", "City", "Rent")]) 
                    | duplicated(df_na[, c("Type", "Area_sqm", "N_rooms", "N_parking_spaces", 
                                           "Street", "Neighborhood", "City", "Rent")], 
                                 fromLast = TRUE), ]

duplicates %>%
  arrange(Street) %>%
  head(10)

```


## 7.4. Removing duplicates from the dataset
```{r echo=TRUE}

df_na <- unique(df_na[, c("Type", "Area_sqm", "N_rooms", "N_bathrooms", "N_parking_spaces", 
                          "Street", "Neighborhood", "City", "Rent")])

duplicates <- df_na[duplicated(df_na[, c("Type", "Area_sqm", "N_rooms", "N_bathrooms", 
                                         "N_parking_spaces", "Street", "Neighborhood", 
                                         "City", "Rent")]) 
                    | duplicated(df_na[, c("Type", "Area_sqm", "N_rooms", "N_bathrooms", 
                                           "N_parking_spaces", "Street", "Neighborhood", 
                                           "City", "Rent")], fromLast = TRUE), ]

duplicates %>%
  arrange(Type) %>%
  head(10)

```



## 7.5. Checking for outliers in 'Area_sqm' column
```{r echo=TRUE}

df_na %>%
  arrange(Area_sqm) %>%
  head(10)

df_na %>%
  arrange(desc(Area_sqm)) %>%
  head(50)

df_na <- df_na %>%
  filter(Area_sqm >= 10 & Area_sqm <= 1000)

df_na %>%
  arrange(Area_sqm) %>%
  head(10)

df_na %>%
  arrange(desc(Area_sqm)) %>%
  head(50)

```


## 7.6. Checking for outliers in 'Neighborhood' column
```{r echo=TRUE}

df_na %>%
  arrange(Neighborhood) %>%
  head(10)

df_na %>%
  arrange(desc(Neighborhood)) %>%
  head(10)

df_na <- df_na %>%
  mutate(Neighborhood = str_remove_all(Neighborhood, "-|\\d")) %>%
  mutate(Neighborhood = str_trim(Neighborhood)) %>%
  select(-Street)
  

df_na %>%
  arrange(Neighborhood) %>%
  head(10)

df_na %>%
  arrange(desc(Neighborhood)) %>%
  head(10)

```


## 7.7. Standardizing the Type column
```{r echo=TRUE}

unique(df_na$Type)

df_na <- df_na %>%
  filter(Type != "Edifício") %>%
  mutate(Type = case_when(
    Type %in% c("Apartamento", "Cobertura", "Flat", "Kitnet/Conjugado") ~ "Condominio",
      TRUE ~ Type
  ))
  
```


## 7.8. Saving the dataframe as an xlsx file
```{r eval=FALSE}

df_cwb_iii <- df_na

file <- "CWB_Dataset_III.xlsx"
folder <- paste0("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Housing/", file)
write.xlsx(df_cwb_iii, folder, rowNames = FALSE)

```

---

# 8. MERGING THE THREE DATASETS


```{r include=FALSE}

df_cwb <- read_excel("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Housing/CWB_Dataset_I.xlsx")
  
df_cwb_ii <- read_excel("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Housing/CWB_Dataset_II.xlsx")

df_cwb_iii <- read_excel("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Housing/CWB_Dataset_III.xlsx")

```


## 8.1. Concatenating the dataframes df_cwb, df_cwb_ii, and df_cwb_iii
```{r echo=TRUE}

df <- rbind(df_cwb, df_cwb_ii, df_cwb_iii)

```


## 8.2. Standardizing the Neighborhood column
```{r echo=TRUE}

extraoficial_n <- as.tibble(unique(df$Neighborhood)) %>%
  rename(Neighborhood = value) %>%
  arrange(Neighborhood)

oficial_n <- read.csv("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Curitiba/Neighborhoods.csv")

result <- as.tibble(c(oficial_n$Neighborhood,
            extraoficial_n$Neighborhood)) %>%
  rename(Neighborhood = value) %>%
  arrange(Neighborhood)

result <- result %>%
  group_by(Neighborhood) %>%
  mutate(
    Oficial = ifelse(n() > 1, Neighborhood, NA),
    Extraoficial = ifelse(n() == 1, Neighborhood, Neighborhood)
  ) %>%
  slice(1) %>%
  ungroup() %>%
  select(-Neighborhood) %>%
  arrange(Oficial)

df <- df %>%
  filter(!Neighborhood %in% c("Alphaville", "Avenida dos Canarios", "Curitiba",
                              "Colonia Rio Grande", "Rodovia BR", "Rua Jaguariaiva",
                              "Rua Tenente", "Sao Miguel")) %>%
  mutate(Neighborhood = case_when(
    Neighborhood == "Barigui" ~ "Santo Inacio",
    Neighborhood %in% c("Alto da Rua Xv", "Alto da XV", "Alto da XV", "Alto") ~ "Alto da Rua XV",
    Neighborhood == "Caiua" ~ "Capao Raso",
    Neighborhood == "Caximba" ~ "Caximba",
    Neighborhood == "Champagnat" ~ "Bigorrilho",
    Neighborhood %in% c("Cidade Industrial", "Cidade Industrial de Curitiba", "Itatiaia",
                        "Neoville") ~ "CIC",
    Neighborhood == "Coronel Servando de Loyola e Silva Barreirinha" ~ "Barreirinha",
    Neighborhood == "Ecoville" ~ "Mossungue",
    Neighborhood == "Jardim Schaffer" ~ "Vista Alegre",
    Neighborhood == "Lamenha Pequena" ~ "Santa Felicidade",
    Neighborhood == "Riviera" ~ "Riviera",
    Neighborhood == "Rua Major Inacio Gomes da Costa" ~ "Uberaba",
    Neighborhood == "Vila Lindoia" ~ "Lindoia",
    TRUE ~ Neighborhood
  ))

Neighborhoods <- as.tibble(unique(df$Neighborhood)) %>%
  rename(neighborhoods = value) %>%
  arrange(neighborhoods)

head(Neighborhoods, 10)
count(Neighborhoods)

```


## 8.3. Saving the dataframe as an xlsx file
```{r eval=FALSE}

file <- "CWB_Dataset.xlsx"
folder <- paste0("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Housing/", file)
write.xlsx(df, folder, rowNames = FALSE)

```


---

# 9. EXPLORATORY ANALYSIS


## 9.1. Preliminary analysis
```{r echo=TRUE}

summary(df)

str(df)

head(df, 10)

tail(df)

```


