---
title: "Mapas - Curitiba"
author: "Lucas Salamuni"
date: "2024-04-17"
output: html_document
---

# 1. Packages

## 1.1. Retrieving Packages
```{r message=FALSE, warning=FALSE, echo = TRUE}

pacotes <- c("tidyverse", "factoextra", "readxl", "ggplot2", "patchwork", 
             "corrplot", "plotly", "data.table", "EFAtools", "psych",
             "leaflet", "sf", "sp", "mapview", "webshot", "htmltools", 
             "leafem", "viridisLite", "writexl", "rvest", "readr", 
             "stringr", "curl", "magrittr", "RSelenium", "netstat", "wdman") 

if(sum(as.numeric(!pacotes %in% installed.packages())) != 0){ 
  instalador <- pacotes[!pacotes %in% installed.packages()] 
  for(i in 1:length(instalador)) {
    install.packages(instalador, dependencies = T)
    break()}
  sapply(pacotes, require, character = T)
} else {
  sapply(pacotes, require, character = T)
}

```

---

# 2. PCA

## 2.1. Performing the stratification of localities according to Fávero (2005)
```{r echo = TRUE}

df_cwb <- read_excel("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Curitiba/Curitiba_Public_Data.xlsx")

var <- df_cwb %>%
  select(`Pop_SM_%`,
         Renda,
         `Alfab_%`,
         Densidade,
         Cresc_pop) %>%
  as.matrix()

EFAtools::KMO(var)

EFAtools::BARTLETT(var)

pca <- var %>%
  prcomp(center = TRUE,
         scale. = TRUE)

loadings <- pca$rotation
scores <- as.data.frame(pca$x)
variance <- (pca$sdev)^2

scores$Localidade <- df_cwb$Localidade
scores <- scores %>%
  relocate(Localidade, .before = 1)

resumo_pca <- summary(pca)

variancia <- data.frame(PC1 = resumo_pca$importance[2,1],
                        PC2 = resumo_pca$importance[2,2]) %>%
  t() %>%
  as.data.frame() %>%
  rename("Variância Compartilhada" = V1)

scores <- scores %>%
  select(Localidade, PC1, PC2)

loadings <- loadings %>%
  as.data.frame() %>%
  select(PC1, PC2)

estratificacao <- data.frame("Localidade" = df_cwb$Localidade,
                    "Score_Final" = ((scores[,2] * variancia[1,] * (-1)) + 
                                       (scores[,3] * variancia[2,] * (-1)))) %>%
  mutate(Estratificação = case_when(
    Score_Final < -0.01 ~ "Baixo",
    Score_Final > 1.00 ~ "Alto",
    TRUE ~ "Médio"
  ))

estratificacao

file <- "CWB_Estrat.xlsx"
folder <- paste0("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Curitiba/", file)
write_xlsx(estratificacao, folder)

```

---

# 3. Shapefiles

## 3.1. Loading shapefiles for use in the overall map
```{r echo = TRUE}

#Bairros
sf_localidades <- st_read("C:/Users/Lucas/OneDrive/Projeto - FS/Shapefiles - CWB/Localidades/DIVISA_DE_BAIRROS.shp")
st_crs(sf_localidades)
sf_localidades <- st_transform(sf_localidades, "+proj=longlat +datum=WGS84")

#Parques e bosques
sf_parques <- st_read("C:/Users/Lucas/OneDrive/Projeto - FS/Shapefiles - CWB/Parques/PARQUES_E_BOSQUES.shp")
st_crs(sf_parques)
sf_parques <- st_transform(sf_parques, "+proj=longlat +datum=WGS84")

#Praças e jardinetes
sf_pracas <- st_read("C:/Users/Lucas/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Shapefiles/Squares/PRACAS_E_JARDINETES.shp")
st_crs(sf_pracas)
sf_pracas <- st_transform(sf_pracas, "+proj=longlat +datum=WGS84")

#Área verde
sf_verde <- st_read("C:/Users/Lucas/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Shapefiles/Green_Area/AREA_VERDE_2019.shp")
st_crs(sf_verde)
sf_verde <- st_transform(sf_verde, "+proj=longlat +datum=WGS84")

#Ciclovias
sf_ciclovias <- st_read("C:/Users/Lucas/OneDrive/Projeto - FS/Shapefiles - CWB/Ciclovias/CICLOVIA_OFICIAL.shp")
st_crs(sf_ciclovias)
sf_ciclovias <- st_transform(sf_ciclovias, "+proj=longlat +datum=WGS84")

#Terminais
sf_terminais <- st_read("C:/Users/Lucas/OneDrive/Projeto - FS/Shapefiles - CWB/Terminais/TERMINAL_DE_TRANSPORTE.shp")
st_crs(sf_terminais)
sf_terminais <- st_transform(sf_terminais, "+proj=longlat +datum=WGS84")

#Hospitais
sf_hospitais <- st_read("C:/Users/Lucas/OneDrive/Projeto - FS/Shapefiles - CWB/Hospitais/HOSPITAL.shp")
st_crs(sf_hospitais)
sf_hospitais <- st_transform(sf_hospitais, "+proj=longlat +datum=WGS84")

#Ocupações irregulares
sf_irregular <- st_read("C:/Users/Lucas/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Shapefiles/Irregular Settlements/OCUPACAO_IRREGULAR.shp")
st_crs(sf_irregular)
sf_irregular <- st_transform(sf_irregular, "+proj=longlat +datum=WGS84")

#Lagos
sf_lagos <- st_read("C:/Users/Lucas/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Shapefiles/Lakes/HIDRO_LAGOS_LAGOAS_REPRESAS.shp")
st_crs(sf_lagos)
sf_lagos <- st_transform(sf_lagos, "+proj=longlat +datum=WGS84")

#Rios
sf_rios <- st_read("C:/Users/Lucas/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Shapefiles/Rivers/HIDRO_RIOS_PG.shp")
st_crs(sf_rios)
sf_rios <- st_transform(sf_rios, "+proj=longlat +datum=WGS84")

#Escolas públicas
sf_esc_pub <- st_read("C:/Users/Lucas/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Shapefiles/Public Schools/ESCOLA_MUNICIPAL.shp")
st_crs(sf_esc_pub)
sf_esc_pub <- st_transform(sf_esc_pub, "+proj=longlat +datum=WGS84")

```

---

# 4. Mapa

## 4.1. Data wrangling
```{r echo = TRUE}

estratificacao$Localidade <- toupper(estratificacao$Localidade)

estratificacao <- estratificacao %>%
  mutate(NOME = case_when(
    Localidade == "AGUA VERDE" ~ "ÁGUA VERDE",
    Localidade == "AHU" ~ "AHÚ",
    Localidade == "ALTO BOQUEIRAO" ~ "ALTO BOQUEIRÃO",
    Localidade == "ALTO DA GLORIA" ~ "ALTO DA GLÓRIA",
    Localidade == "BOQUEIRAO" ~ "BOQUEIRÃO",
    Localidade == "CAPAO DA IMBUIA" ~ "CAPÃO DA IMBUIA",
    Localidade == "CAPAO RASO" ~ "CAPÃO RASO", 
    Localidade == "CENTRO CIVICO" ~ "CENTRO CÍVICO",
    Localidade == "CIC" ~ "CIDADE INDUSTRIAL DE CURITIBA",
    Localidade == "GUAIRA" ~ "GUAÍRA",
    Localidade == "JARDIM BOTANICO" ~ "JARDIM BOTÂNICO",
    Localidade == "JARDIM DAS AMERICAS" ~ "JARDIM DAS AMÉRICAS",
    Localidade == "JUVEVE" ~ "JUVEVÊ",
    Localidade == "LINDOIA" ~ "LINDÓIA",
    Localidade == "MERCES" ~ "MERCÊS",
    Localidade == "MOSSUNGUE" ~ "MOSSUNGUÊ",
    Localidade == "PORTAO" ~ "PORTÃO",
    Localidade == "REBOUCAS" ~ "REBOUÇAS",
    Localidade == "SANTA CANDIDA" ~ "SANTA CÂNDIDA",
    Localidade == "SANTA QUITERIA" ~ "SANTA QUITÉRIA",
    Localidade == "SANTO INACIO" ~ "SANTO INÁCIO",
    Localidade == "SAO BRAZ" ~ "SÃO BRAZ",
    Localidade == "SAO FRANCISCO" ~ "SÃO FRANCISCO",
    Localidade == "SAO JOAO" ~ "SÃO JOÃO",
    Localidade == "SAO LOURENCO" ~ "SÃO LOURENÇO",
    Localidade == "SAO MIGUEL" ~ "SÃO MIGUEL",
    Localidade == "SEMINARIO" ~ "SEMINÁRIO",
    Localidade == "SITIO CERCADO" ~ "SÍTIO CERCADO",
    Localidade == "TABOAO" ~ "TABOÃO",
    Localidade == "TARUMA" ~ "TARUMÃ",
    Localidade == "UMBARA" ~ "UMBARÁ",
    TRUE ~ Localidade
  )) %>%
  relocate(NOME, .after = "Localidade")

sf_localidades <- merge(sf_localidades, estratificacao,
                        by = "NOME") %>%
  select(-Localidade, NOME) %>%
  relocate(Score_Final, .after = "NOME") %>%
  relocate(Estratificação, .after = "Score_Final")

df_cwb$Localidade <- toupper(df_cwb$Localidade)

df_cwb <- df_cwb %>%
  mutate(NOME = case_when(
    Localidade == "AGUA VERDE" ~ "ÁGUA VERDE",
    Localidade == "AHU" ~ "AHÚ",
    Localidade == "ALTO BOQUEIRAO" ~ "ALTO BOQUEIRÃO",
    Localidade == "ALTO DA GLORIA" ~ "ALTO DA GLÓRIA",
    Localidade == "BOQUEIRAO" ~ "BOQUEIRÃO",
    Localidade == "CAPAO DA IMBUIA" ~ "CAPÃO DA IMBUIA",
    Localidade == "CAPAO RASO" ~ "CAPÃO RASO", 
    Localidade == "CENTRO CIVICO" ~ "CENTRO CÍVICO",
    Localidade == "CIC" ~ "CIDADE INDUSTRIAL DE CURITIBA",
    Localidade == "GUAIRA" ~ "GUAÍRA",
    Localidade == "JARDIM BOTANICO" ~ "JARDIM BOTÂNICO",
    Localidade == "JARDIM DAS AMERICAS" ~ "JARDIM DAS AMÉRICAS",
    Localidade == "JUVEVE" ~ "JUVEVÊ",
    Localidade == "LINDOIA" ~ "LINDÓIA",
    Localidade == "MERCES" ~ "MERCÊS",
    Localidade == "MOSSUNGUE" ~ "MOSSUNGUÊ",
    Localidade == "PORTAO" ~ "PORTÃO",
    Localidade == "REBOUCAS" ~ "REBOUÇAS",
    Localidade == "SANTA CANDIDA" ~ "SANTA CÂNDIDA",
    Localidade == "SANTA QUITERIA" ~ "SANTA QUITÉRIA",
    Localidade == "SANTO INACIO" ~ "SANTO INÁCIO",
    Localidade == "SAO BRAZ" ~ "SÃO BRAZ",
    Localidade == "SAO FRANCISCO" ~ "SÃO FRANCISCO",
    Localidade == "SAO JOAO" ~ "SÃO JOÃO",
    Localidade == "SAO LOURENCO" ~ "SÃO LOURENÇO",
    Localidade == "SAO MIGUEL" ~ "SÃO MIGUEL",
    Localidade == "SEMINARIO" ~ "SEMINÁRIO",
    Localidade == "SITIO CERCADO" ~ "SÍTIO CERCADO",
    Localidade == "TABOAO" ~ "TABOÃO",
    Localidade == "TARUMA" ~ "TARUMÃ",
    Localidade == "UMBARA" ~ "UMBARÁ",
    TRUE ~ Localidade
  )) %>%
  relocate(NOME, .after = "Localidade") %>%
  select(-Localidade)

sf_localidades <- merge(sf_localidades, df_cwb,
                        by = "NOME")

sf_localidades$Estratificação <- factor(sf_localidades$Estratificação,
                                        levels = c("Baixo", "Médio", "Alto"))


sf_terminais <- sf_terminais %>%
  mutate(NOME_COMPL = iconv(NOME_COMPL, from = "latin1", to = "UTF-8")) %>%
  mutate(NOME = iconv(NOME, from = "latin1", to = "UTF-8")) %>%
  mutate(BAIRRO = iconv(BAIRRO, from = "latin1", to = "UTF-8"))
      
```


## 4.2. Palettes
```{r echo = TRUE}

palette <- colorFactor(palette = c("blue", "gold", "red"),
                       domain = sf_localidades$Estratificação)

viridis <- viridis(20)

palette_i <- colorNumeric(palette = "YlOrBr",
                          domain = sf_localidades$Populacao,
                          na.color = "transparent")

palette_ii <- colorNumeric(palette = "Blues",
                           domain = sf_localidades$`Densidade_ab/ha`,
                           na.color = "transparent")

```


## 4.3. Texts
```{r echo = TRUE}

text_bairros <- paste(
  "Bairro: ", sf_localidades$NOME, "<br/>",
  "População: ", sf_localidades$Populacao,
  sep = "") %>%
  lapply(htmltools::HTML)

text_parks <- paste(
  "Nome: ", sf_parques$TEXTO_MAPA, "<br/>",
  "Tipo: ", sf_parques$TIPO,
  sep = "") %>%
  lapply(htmltools::HTML)

text_lakes <- paste(
  "Nome: ", sf_lagos$NOME, "<br/>",
  "Tipo: ", sf_lagos$TIPO,
  sep = "") %>%
  lapply(htmltools::HTML)

text_rivers <- paste(
  "Nome: ", sf_rios$NOME, "<br/>",
  "Tipo: ", sf_rios$TIPO,
  sep = "") %>%
  lapply(htmltools::HTML)

text_density <- paste(
  "Nome: ", sf_localidades$NOME, "<br/>",
  "População: ", sf_localidades$`Densidade_ab/ha`,
  sep = "") %>%
  lapply(htmltools::HTML)

text_estratification <- paste(
  "Bairro: ", sf_localidades$NOME, "<br/>",
  "Estratificação: ", sf_localidades$Estratificação,
  sep = "") %>%
  lapply(htmltools::HTML)

```


## 4.4. Icons
```{r echo = TRUE}

icone_hospitais <- awesomeIcons(
  icon = "plus",
  iconColor = "white",
  library = "glyphicon",
  markerColor = "red"
)

icone_terminais <- awesomeIcons(
  icon = "bus",
  iconColor = "white",
  library = "fa",
  markerColor = "blue"
)

icone_escolas_publicas <- awesomeIcons(
  icon = "book",
  iconColor = "white",
  library = "glyphicon",
  markerColor = "orange"
)

```


## 4.5. Map providers
```{r echo = TRUE}

providers <- c("OpenStreetMap", "Esri.WorldImagery")

```


## 4.6. UTM -> lat/long
```{r echo = TRUE}

utm_proj <- "+proj=utm +zone=22 +datum=WGS84"

sf_hospitais <- st_transform(sf_hospitais, "+proj=longlat +datum=WGS84")

sf_hospitais$Longitude <- st_coordinates(sf_hospitais)[, "X"]
sf_hospitais$Latitude <- st_coordinates(sf_hospitais)[, "Y"]

sf_terminais <- st_transform(sf_terminais, "+proj=longlat +datum=WGS84")

sf_terminais$Longitude <- st_coordinates(sf_terminais)[, "X"]
sf_terminais$Latitude <- st_coordinates(sf_terminais)[, "Y"]

sf_esc_pub <- st_transform(sf_esc_pub, "+proj=longlat +datum=WGS84")

sf_esc_pub$Longitude <- st_coordinates(sf_esc_pub)[, "X"]
sf_esc_pub$Latitude <- st_coordinates(sf_esc_pub)[, "Y"]

```


## 4.7. Map
```{r echo = TRUE}

mapa <- leaflet()
for(i in 1:length(providers)){
  mapa <- mapa %>%
    addProviderTiles(providers[i],
                     group = providers[i])
}

mapa <- mapa %>%
  addProviderTiles("OpenStreetMap") %>%
  addPolygons(data = sf_localidades,
              group = "Limite de Bairros",
              fillColor = "transparent",
              smoothFactor = 0.5,
              opacity = 1,
              stroke = TRUE,
              weight = 1,
              color = "black",
              highlight = highlightOptions(color = "white",
                                           weight = 2,
                                           bringToFront = TRUE,
                                           stroke = TRUE),
              label = text_bairros,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "13px",
                direction = "auto"
              )) %>%
  addPolygons(data = sf_parques,
              group = "Área Verde",
              stroke = FALSE,
              fillColor = "green",
              color = "transparent",
              fillOpacity = 0.7,
              highlight = highlightOptions(color = "darkgreen",
                                           weight = 3,
                                           bringToFront = TRUE,
                                           stroke = TRUE),
              label = text_parks,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "13px",
                direction = "auto"
              )) %>%
  addPolygons(data = sf_pracas,
              group = "Área Verde",
              stroke = FALSE,
              fillColor = "green",
              color = "transparent",
              fillOpacity = 0.7,
              highlight = highlightOptions(color = "darkgreen",
                                           weight = 3,
                                           bringToFront = TRUE,
                                           stroke = TRUE),
              label = sf_pracas$NOME,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "13px",
                direction = "auto"
              )) %>%
  addPolygons(data = sf_lagos,
              group = "Hidrografia",
              stroke = FALSE,
              fillColor = "blue",
              color = "transparent",
              fillOpacity = 0.7,
              highlight = highlightOptions(color = "darkblue",
                                           weight = 3,
                                           bringToFront = TRUE,
                                           stroke = TRUE),
              label = text_lakes,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "13px",
                direction = "auto"
              )) %>%
  addPolygons(data = sf_rios,
              group = "Hidrografia",
              stroke = FALSE,
              fillColor = "blue",
              color = "transparent",
              fillOpacity = 0.7,
              highlight = highlightOptions(color = "darkblue",
                                           weight = 3,
                                           bringToFront = TRUE,
                                           stroke = TRUE),
              label = text_rivers,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "13px",
                direction = "auto"
              )) %>%
  addPolygons(data = sf_irregular,
              group = "Ocupação Irregular",
              stroke = FALSE,
              fillColor = "red",
              color = "transparent",
              fillOpacity = 0.7,
              highlight = highlightOptions(color = "white",
                                           weight = 3,
                                           bringToFront = TRUE,
                                           stroke = TRUE),
              label = sf_irregular$NOME,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "13px",
                direction = "auto"
              )) %>%
  addAwesomeMarkers(group = "Hospitais",
                    data = sf_hospitais,
                    lng = ~Longitude,
                    lat = ~Latitude,
                    popup = ~NOME_COMPL,
                    icon = icone_hospitais
                    ) %>%
  addAwesomeMarkers(group = "Terminais de Ônibus",
                    data = sf_terminais,
                    lng = ~Longitude,
                    lat = ~Latitude,
                    popup = ~NOME_COMPL,
                    icon = icone_terminais
                    ) %>%
  addAwesomeMarkers(group = "Escolas Municipais",
                    data = sf_esc_pub,
                    lng = ~Longitude,
                    lat = ~Latitude,
                    popup = ~NOME_MAPA,
                    icon = icone_escolas_publicas
                    ) %>%
  addPolygons(data = sf_localidades,
              group = "População",
              fillColor = ~palette_i(sf_localidades$Populacao),
              smoothFactor = 0.5,
              opacity = 1,
              stroke = TRUE,
              weight = 1,
              fillOpacity = 0.5,
              color = "black",
              highlight = highlightOptions(color = "white",
                                           weight = 2,
                                           bringToFront = TRUE,
                                           stroke = TRUE),
              label = text_bairros,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "13px",
                direction = "auto"
              )) %>%
  addPolygons(data = sf_localidades,
              group = "Densidade",
              fillColor = ~palette_ii(sf_localidades$`Densidade_ab/ha`),
              smoothFactor = 0.5,
              opacity = 1,
              stroke = TRUE,
              weight = 1,
              fillOpacity = 0.5,
              color = "black",
              highlight = highlightOptions(color = "white",
                                           weight = 2,
                                           bringToFront = TRUE,
                                           stroke = TRUE),
              label = text_density,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "13px",
                direction = "auto"
              )) %>%
  addPolygons(data = sf_localidades,
              group = "Estratificação de Bairros",
              fillColor = ~palette(sf_localidades$Estratificação),
              smoothFactor = 0.5,
              opacity = 1,
              stroke = TRUE,
              weight = 1,
              fillOpacity = 0.5,
              color = "black",
              highlight = highlightOptions(color = "white",
                                           weight = 2,
                                           bringToFront = TRUE,
                                           stroke = TRUE),
              label = text_estratification,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "13px",
                direction = "auto"
              )) %>%
  addLegend(group = "Estratificação de Bairros",
            data = sf_localidades,
            pal = palette,
            values = ~Estratificação,
            opacity = 1,
            title = "Estratificação",
            position = "bottomright") %>%
  addLegend(group = "População",
            data = sf_localidades,
            pal = palette_i,
            values = ~Populacao,
            opacity = 1,
            title = "População",
            position = "bottomright") %>%
  addLegend(group = "Densidade",
            data = sf_localidades,
            pal = palette_ii,
            values = ~`Densidade_ab/ha`,
            opacity = 1,
            title = "Densidade",
            position = "bottomright") %>%
  addLayersControl(
    baseGroups = providers,
    overlayGroups = c("Limite de Bairros",
                      "Área Verde",
                      "Hidrografia",
                      "Ocupação Irregular",
                      "Hospitais",
                      "Terminais de Ônibus",
                      "Escolas Municipais",
                      "População",
                      "Densidade",
                      "Estratificação de Bairros"),
    position = "topleft",
    options = layersControlOptions(collapsed = TRUE)) %>%
  addMeasure(primaryLengthUnit = "meters",
             primaryAreaUnit = "sqmeters",
             position = "bottomleft")
  
mapa

```

---

# 5. Creating the new datasets

```{r include = FALSE}

escolas_particulares <- read_excel("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Curitiba/Private_schools.xlsx")

```


# 5.1. Web scraping of private school data
```{r eval = FALSE}

selenium()
selenium_object <- selenium(retcommand = TRUE,
                            check = FALSE)
rs_driver_object <- rsDriver(browser = "chrome",
                             chromever = "125.0.6422.60",
                             verbose = FALSE,
                             port = free_port())

extract_school_info <- function() {
  page_source <- remDr$getPageSource()[[1]] 
  df <- read_html(page_source) %>%
    html_nodes("h2") %>%
    html_text() %>%
    tibble(NOME = .) %>%
    bind_cols(
      read_html(page_source) %>%
        html_nodes("p") %>%
        html_text() %>%
        tibble(BAIRRO = .) %>%
        slice(2:31) %>%
        mutate(BAIRRO = str_extract(BAIRRO, "[^,]+")) %>%
        mutate(BAIRRO = toupper(BAIRRO)) %>%
        mutate(BAIRRO = str_trim(BAIRRO)) %>%
        mutate(BAIRRO = case_when(
          BAIRRO == "AGUA VERDE" ~ "ÁGUA VERDE",
          BAIRRO == "AHU" ~ "AHÚ",
          BAIRRO == "ALTO BOQUEIRAO" ~ "ALTO BOQUEIRÃO",
          BAIRRO == "ALTO DA GLORIA" ~ "ALTO DA GLÓRIA",
          BAIRRO == "BOQUEIRAO" ~ "BOQUEIRÃO",
          BAIRRO == "CAPAO DA IMBUIA" ~ "CAPÃO DA IMBUIA",
          BAIRRO == "CAPAO RASO" ~ "CAPÃO RASO", 
          BAIRRO == "CENTRO CIVICO" ~ "CENTRO CÍVICO",
          BAIRRO == "CIC" ~ "CIDADE INDUSTRIAL DE CURITIBA",
          BAIRRO == "GUAIRA" ~ "GUAÍRA",
          BAIRRO == "JARDIM BOTANICO" ~ "JARDIM BOTÂNICO",
          BAIRRO == "JARDIM DAS AMERICAS" ~ "JARDIM DAS AMÉRICAS",
          BAIRRO == "JUVEVE" ~ "JUVEVÊ",
          BAIRRO == "LINDOIA" ~ "LINDÓIA",
          BAIRRO == "MERCES" ~ "MERCÊS",
          BAIRRO == "MOSSUNGUE" ~ "MOSSUNGUÊ",
          BAIRRO == "PORTAO" ~ "PORTÃO",
          BAIRRO == "REBOUCAS" ~ "REBOUÇAS",
          BAIRRO == "SANTA CANDIDA" ~ "SANTA CÂNDIDA",
          BAIRRO == "SANTA QUITERIA" ~ "SANTA QUITÉRIA",
          BAIRRO == "SANTO INACIO" ~ "SANTO INÁCIO",
          BAIRRO == "SAO BRAZ" ~ "SÃO BRAZ",
          BAIRRO == "SAO FRANCISCO" ~ "SÃO FRANCISCO",
          BAIRRO == "SAO JOAO" ~ "SÃO JOÃO",
          BAIRRO == "SAO LOURENCO" ~ "SÃO LOURENÇO",
          BAIRRO == "SAO MIGUEL" ~ "SÃO MIGUEL",
          BAIRRO == "SEMINARIO" ~ "SEMINÁRIO",
          BAIRRO == "SITIO CERCADO" ~ "SÍTIO CERCADO",
          BAIRRO == "TABOAO" ~ "TABOÃO",
          BAIRRO == "TARUMA" ~ "TARUMÃ",
          BAIRRO == "UMBARA" ~ "UMBARÁ",
          TRUE ~ BAIRRO
          ))
    )
  return(df)
}

iterations <- 16 
school_source_cwb <- list()
for (page_number in 1:iterations) {
  remDr <- rs_driver_object$client
  if (page_number == 1) {
    url <- "https://escolas.com.br/particulares/pr/curitiba"
  } else {
    url <- paste0("https://escolas.com.br/particulares/pr/curitiba?pagina=", page_number)
  }
  remDr$open()
  remDr$navigate(url)
  df <- extract_school_info()
  school_source_cwb[[page_number]] <- df
  remDr$close()
}

escolas_particulares <- do.call(rbind, school_source_cwb)

```


## 5.2. Accessing datasets of homicides and shopping malls by neighborhood
```{r eval = FALSE}

homicidios <- read_excel("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Curitiba/Homicides.xlsx")

shoppings <- read_excel("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Curitiba/Shopping_centers.xlsx")

```


## 5.3. *info_bairros*
```{r eval = FALSE}

info_bairros <- df_cwb %>%
  select(NOME, Populacao, `Densidade_ab/ha`) %>%
  rename(BAIRRO = NOME,
         POPULACAO = Populacao,
         DENSIDADE = `Densidade_ab/ha`)

hospitais <- sf_hospitais %>%
  select(BAIRRO) %>%
  st_drop_geometry() %>%
  mutate(BAIRRO = toupper(BAIRRO)) %>%
  count(BAIRRO) %>%
  rename(N_HOSPITAIS = n) %>%
  arrange(BAIRRO) %>%
  as_tibble()

irregular <- sf_irregular %>%
  select(BAIRRO, SHAPE_AREA) %>%
  st_drop_geometry() %>%
  group_by(BAIRRO) %>%
  summarise(AREA_IRREGULAR = sum(SHAPE_AREA)) %>%
  arrange(BAIRRO) %>%
  as_tibble()

terminais <- sf_terminais %>%
  select(BAIRRO) %>%
  mutate(BAIRRO = toupper(BAIRRO)) %>%
  st_drop_geometry() %>%
  count(BAIRRO) %>%
  rename(N_TERMINAIS = n)

escolas_publicas <- sf_esc_pub %>%
  select(BAIRRO) %>%
  mutate(BAIRRO = toupper(BAIRRO)) %>%
  st_drop_geometry() %>%
  count(BAIRRO) %>%
  rename(N_PUBLIC_SCHOOLS = n)

escolas_particulares <- escolas_particulares %>%
  group_by(BAIRRO) %>%
  summarise(N_PRIVATE_SCHOOLS = n()) %>%
  arrange(BAIRRO) %>%
  as_tibble()

area_verde <- sf_verde %>% 
  select(nm_bairro, Shape_Area) %>%
  mutate(BAIRRO = toupper(nm_bairro)) %>%
  st_drop_geometry() %>%
  group_by(BAIRRO) %>%
  summarise(AREA_VERDE = sum(Shape_Area)) %>%
  arrange(BAIRRO) %>%
  as_tibble()

localidades <- sf_localidades %>%
  select(NOME, SHAPE_AREA) %>%
  rename(BAIRRO = NOME,
         AREA = SHAPE_AREA) %>%
  st_drop_geometry() %>%
  as_tibble()

shoppings <- shoppings %>%
  group_by(BAIRRO) %>%
  summarise(N_SHOPPINGS = n()) %>%
  arrange(BAIRRO) %>%
  as_tibble()

homicidios <- homicidios %>%
  select(BAIRRO) %>%
  group_by(BAIRRO) %>%
  summarise(N_HOMICIDIOS = n()) %>%
  arrange(BAIRRO) %>%
  as_tibble()

lista_dfs <- list(hospitais, irregular, area_verde, terminais, escolas_publicas, 
                  escolas_particulares, shoppings, homicidios, localidades) 

info_bairros <- reduce(lista_dfs, ~left_join(.x, .y, by = "BAIRRO"),
                       .init = info_bairros)

info_bairros <- info_bairros %>%
  mutate(AREA_IRREGULAR = round(AREA_IRREGULAR, 2)) %>%
  mutate_at(vars(N_HOSPITAIS, AREA_IRREGULAR, N_TERMINAIS, N_PUBLIC_SCHOOLS,
                 N_PRIVATE_SCHOOLS, N_HOMICIDIOS, N_SHOPPINGS),
            ~ifelse(is.na(.), 0, .)) %>%
  mutate(HOSP_1000 = round((N_HOSPITAIS*1000)/POPULACAO, 5),
         TERM_1000 = round((N_TERMINAIS*1000)/POPULACAO, 5),
         SHOP_1000 = round((N_SHOPPINGS*1000)/POPULACAO, 5),
         ESC_PUB_1000 = round((N_PUBLIC_SCHOOLS*1000)/POPULACAO, 5),
         ESC_PRI_1000 = round((N_PRIVATE_SCHOOLS*1000)/POPULACAO, 5),
         HOMI_1000 = round((N_HOMICIDIOS*1000)/POPULACAO, 5),
         `AREA_VERDE_%` = round((AREA_VERDE*100)/AREA, 2),
         `AREA_IRREGULAR_%` = round((AREA_IRREGULAR*100)/AREA, 2)) %>%
  mutate_at(vars(HOSP_1000, TERM_1000, SHOP_1000, ESC_PUB_1000, ESC_PRI_1000,
                 HOMI_1000, `AREA_VERDE_%`, `AREA_IRREGULAR_%`),
            ~ifelse(is.infinite(.), 0, .)) %>%
  select(-c(N_HOSPITAIS, N_TERMINAIS, AREA_IRREGULAR, AREA, N_PUBLIC_SCHOOLS, 
            N_PRIVATE_SCHOOLS, N_HOMICIDIOS, N_SHOPPINGS, AREA_VERDE)) %>%
  as_tibble()

file <- "Info_Bairros.xlsx"
folder <- paste0("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Curitiba/", file)
write_xlsx(info_bairros, folder)

```


## 5.4. Merging the information with the main dataset
```{r eval = FALSE}

housing_df <- read_excel("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Housing/CWB_Housing_Dataset.xlsx")

housing_df <- housing_df %>%
  mutate(BAIRRO = toupper(Neighborhood)) %>%
  select(-c(Neighborhood, City)) %>%
  relocate(BAIRRO, .before = "Type") %>%
  mutate(BAIRRO = case_when(
    BAIRRO == "AGUA VERDE" ~ "ÁGUA VERDE",
    BAIRRO == "AHU" ~ "AHÚ",
    BAIRRO == "ALTO BOQUEIRAO" ~ "ALTO BOQUEIRÃO",
    BAIRRO == "ALTO DA GLORIA" ~ "ALTO DA GLÓRIA",
    BAIRRO == "BOQUEIRAO" ~ "BOQUEIRÃO",
    BAIRRO == "CAPAO DA IMBUIA" ~ "CAPÃO DA IMBUIA",
    BAIRRO == "CAPAO RASO" ~ "CAPÃO RASO", 
    BAIRRO == "CENTRO CIVICO" ~ "CENTRO CÍVICO",
    BAIRRO == "CIC" ~ "CIDADE INDUSTRIAL DE CURITIBA",
    BAIRRO == "GUAIRA" ~ "GUAÍRA",
    BAIRRO == "JARDIM BOTANICO" ~ "JARDIM BOTÂNICO",
    BAIRRO == "JARDIM DAS AMERICAS" ~ "JARDIM DAS AMÉRICAS",
    BAIRRO == "JUVEVE" ~ "JUVEVÊ",
    BAIRRO == "LINDOIA" ~ "LINDÓIA",
    BAIRRO == "MERCES" ~ "MERCÊS",
    BAIRRO == "MOSSUNGUE" ~ "MOSSUNGUÊ",
    BAIRRO == "PORTAO" ~ "PORTÃO",
    BAIRRO == "REBOUCAS" ~ "REBOUÇAS",
    BAIRRO == "SANTA CANDIDA" ~ "SANTA CÂNDIDA",
    BAIRRO == "SANTA QUITERIA" ~ "SANTA QUITÉRIA",
    BAIRRO == "SANTO INACIO" ~ "SANTO INÁCIO",
    BAIRRO == "SAO BRAZ" ~ "SÃO BRAZ",
    BAIRRO == "SAO FRANCISCO" ~ "SÃO FRANCISCO",
    BAIRRO == "SAO JOAO" ~ "SÃO JOÃO",
    BAIRRO == "SAO LOURENCO" ~ "SÃO LOURENÇO",
    BAIRRO == "SAO MIGUEL" ~ "SÃO MIGUEL",
    BAIRRO == "SEMINARIO" ~ "SEMINÁRIO",
    BAIRRO == "SITIO CERCADO" ~ "SÍTIO CERCADO",
    BAIRRO == "TABOAO" ~ "TABOÃO",
    BAIRRO == "TARUMA" ~ "TARUMÃ",
    BAIRRO == "UMBARA" ~ "UMBARÁ",
    TRUE ~ BAIRRO
  ))

housing_df <- left_join(housing_df, info_bairros, by = "BAIRRO")

housing_df <- housing_df %>%
  rename(Population = POPULACAO) %>%
  rename(Density = DENSIDADE) %>%
  rename(Neighborhood = BAIRRO) %>%
  rename(Hosp_1000 = HOSP_1000) %>%
  rename(Term_1000 = TERM_1000) %>%
  rename(Shop_1000 = SHOP_1000) %>%
  rename(School_Public_1000 = ESC_PUB_1000) %>%
  rename(School_Private_1000 = ESC_PRI_1000) %>%
  rename(Homi_1000 = HOMI_1000) %>%
  rename(`Green_Area_%` = `AREA_VERDE_%`) %>%
  rename(`Irregular_settelments_%` = `AREA_IRREGULAR_%`) %>%
  relocate(Hosp_1000, .after = "N_parking_spaces") %>%
  relocate(Term_1000, .after = "Hosp_1000") %>%
  relocate(Shop_1000, .after = "Term_1000") %>%
  relocate(School_Public_1000, .after = "Shop_1000") %>%
  relocate(School_Private_1000, .after = "School_Public_1000") %>%
  relocate(`Green_Area_%`, .after = "School_Private_1000") %>%
  relocate(`Irregular_settelments_%`, .after = "Green_Area_%") %>%
  relocate(Homi_1000, .after = "Irregular_settelments_%") %>%
  relocate(Population, .after = "Neighborhood") %>%
  relocate(Density, .after = "Population")

estratificacao <- estratificacao %>%
  rename(Neighborhood = NOME)

housing_df <- left_join(housing_df, estratificacao, by = "Neighborhood")

housing_df <- housing_df %>%
  select(-c(Score_Final, Localidade)) %>%
  rename(Tier = Estratificação) %>%
  relocate(Tier, .after = "Neighborhood") %>%
  mutate(Type = as.factor(Type))

```


## 5.5. Separating the data frames by stratification for later regression
```{r eval = FALSE}

High_tier <- housing_df %>%
  filter(Tier == "Alto")

file <- "High_tier.xlsx"
folder <- paste0("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Housing/", file)
write_xlsx(High_tier, folder)

Medium_tier <- housing_df %>%
  filter(Tier == "Médio")

file <- "Medium_tier.xlsx"
folder <- paste0("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Housing/", file)
write_xlsx(Medium_tier, folder)

Low_tier <- housing_df %>%
  filter(Tier == "Baixo")

file <- "Low_tier.xlsx"
folder <- paste0("C:/Users/lsala/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Housing/", file)
write_xlsx(Low_tier, folder)

```


