---
title: "V1_Regressão"
author: "Lucas Salamuni"
date: "2024-05-04"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

# 1. Packages

## 1.1. Retrieving Packages
```{r message=FALSE, warning=FALSE, echo = TRUE}

pacotes <- c("tidyverse", "factoextra", "readxl", "ggplot2", "writexl",
             "cowplot", "car", "lmtest", "psych", "car", "tseries",
             "whitestrap", "jtools", "sandwich", "foreign", "plm", "gap") 

if(sum(as.numeric(!pacotes %in% installed.packages())) != 0){ 
  instalador <- pacotes[!pacotes %in% installed.packages()] 
  for(i in 1:length(instalador)) {
    install.packages(instalador, dependencies = T)
    break()}
  sapply(pacotes, require, character = T)
} else {
  sapply(pacotes, require, character = T)
}

```

---

# 2. Logarithmic Function Form - Second Stage of Rosen
* NOTE 1 = The second stage of Rosen can be summarized as the calculation of the implicit price derivative of a characteristic through the partial derivative of the previous stage's regression with respect to that same characteristic. Thus, the dependent variable in the second regression is the implicit marginal price, which can be represented as:

* Low Stratification:
$$ \frac{p}{m^2} = \frac{0,665 \cdot p}{\text{AREA}} $$

* Medium Stratification:
$$ \frac{p}{m^2} = \frac{0,495 \cdot p}{\text{AREA}} $$

* High Stratification:
$$ \frac{p}{m^2} = \frac{0,529 \cdot p}{\text{AREA}} $$

* NOTE 2 = Equations according to Fávero (2005) and Fávero et al. (2018).

## 2.1. Low Stratification

### 2.1.1. New Dependent Variable and Second Stage Regression
```{r echo = TRUE}

low_tier <- read_excel("C:/Users/Lucas/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Housing/Low_tier.xlsx")

low_tier <- low_tier %>%
  mutate(`P/M` = Rent/Area_sqm)

quantile(low_tier$`P/M`)

Q1 <- quantile(low_tier$`P/M`)[2]
Q3 <- quantile(low_tier$`P/M`)[4]

IQR <- IQR(low_tier$`P/M`)

below <- (Q1 - (0.85) * IQR)
below
above <- (Q3 + (0.85) * IQR)
above

low_tier <- low_tier %>%
  filter(`P/M` >= below & `P/M` <= above) %>%
  select(-`P/M`)

low_tier <- low_tier %>%
  mutate(`p/m²` = (0.66559*Rent)/Area_sqm)

count(low_tier)

low_tier_ln <- low_tier %>%
  mutate_at(vars(Area_sqm, N_rooms, N_bathrooms, N_parking_spaces, 
                 Hosp_1000, Term_1000, Shop_1000, `Green_Area_%`, 
                 `Irregular_settelments_%`, School_Public_1000, 
                 School_Private_1000, Homi_1000,
                 Population, Density, Rent, `p/m²`), log) %>%
  mutate_at(vars(Area_sqm, N_rooms, N_bathrooms, N_parking_spaces, 
                 Hosp_1000, Term_1000, Shop_1000, `Green_Area_%`, 
                 `Irregular_settelments_%`, School_Public_1000, 
                 School_Private_1000, Homi_1000,
                 Population, Density, Rent, `p/m²`),
            ~ifelse(is.infinite(.), 0, .)) %>%
  relocate(Rent, .before = "Area_sqm") %>%
  select(-c(Tier, Neighborhood, Type, Term_1000, Homi_1000,
                 Population, Rent))

low_lm_ln <- lm(`p/m²` ~ ., 
                data = low_tier_ln)

plot(low_lm_ln)
qplot(low_lm_ln$residuals)

shapiro.test(low_lm_ln$residuals) 
jarque.bera.test(low_lm_ln$residuals)

bptest(low_lm_ln) 
white_test(low_lm_ln) 

durbinWatsonTest(low_lm_ln) 

pairs.panels(low_tier_ln) 
car::vif(low_lm_ln) 

summary(low_lm_ln)

```

### 2.1.2. Addressing the heteroscedasticity of the model using the Newey-West procedure.
```{r echo = TRUE}

coeftest(low_lm_ln, vcov = NeweyWest(low_lm_ln))

```

## 2.2. Medium Stratification

### 2.2.1. New Dependent Variable and Second Stage Regression
```{r echo = TRUE}

mid_tier <- read_excel("C:/Users/Lucas/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Housing/Medium_tier.xlsx")

mid_tier <- mid_tier %>%
  mutate(`P/M` = Rent/Area_sqm)

quantile(mid_tier$`P/M`)

Q1 <- quantile(mid_tier$`P/M`)[2]
Q3 <- quantile(mid_tier$`P/M`)[4]

IQR <- IQR(mid_tier$`P/M`)

below <- (Q1 - (0.85) * IQR)
below
above <- (Q3 + (0.85) * IQR)
above

mid_tier <- mid_tier %>%
  filter(`P/M` >= below & `P/M` <= above) %>%
  select(-`P/M`)

mid_tier <- mid_tier %>%
  mutate(`p/m²` = (0.49592*Rent)/Area_sqm)

count(mid_tier)

mid_tier_ln <- mid_tier %>%
  mutate_at(vars(Area_sqm, N_rooms, N_bathrooms, N_parking_spaces, 
                 Hosp_1000, Term_1000, Shop_1000, `Green_Area_%`, 
                 `Irregular_settelments_%`, School_Public_1000, 
                 School_Private_1000, Homi_1000,
                 Population, Density, Rent, `p/m²`), log) %>%
  mutate_at(vars(Area_sqm, N_rooms, N_bathrooms, N_parking_spaces, 
                 Hosp_1000, Term_1000, Shop_1000, `Green_Area_%`, 
                 `Irregular_settelments_%`, School_Public_1000, 
                 School_Private_1000, Homi_1000,
                 Population, Density, Rent, `p/m²`),
            ~ifelse(is.infinite(.), 0, .)) %>%
  relocate(Rent, .before = "Area_sqm") %>%
  select(-c(Tier, Neighborhood, Type, Term_1000, Homi_1000,
                 Population, Rent))

mid_lm_ln <- lm(`p/m²` ~ ., 
                data = mid_tier_ln)

plot(mid_lm_ln)
qplot(mid_lm_ln$residuals)

shapiro.test(mid_lm_ln$residuals) 
jarque.bera.test(mid_lm_ln$residuals)

bptest(mid_lm_ln)
white_test(mid_lm_ln) 

durbinWatsonTest(mid_lm_ln)

pairs.panels(mid_tier_ln) 
car::vif(mid_lm_ln)

summary(mid_lm_ln)

```

### 2.2.2. Addressing the heteroscedasticity of the model using the Newey-West procedure.
```{r echo = TRUE}

coeftest(mid_lm_ln, vcov = NeweyWest(mid_lm_ln))

```

## 2.3. High Stratification

### 2.3.1. New Dependent Variable and Second Stage Regression
```{r echo = TRUE}

high_tier <- read_excel("C:/Users/Lucas/OneDrive/Lucas Salamuni/Universidades/USP/ZZZ - TCC/Datasets/Housing/High_tier.xlsx")

high_tier <- high_tier %>%
  mutate(`P/M` = Rent/Area_sqm)

quantile(high_tier$`P/M`)

Q1 <- quantile(high_tier$`P/M`)[2]
Q3 <- quantile(high_tier$`P/M`)[4]

IQR <- IQR(high_tier$`P/M`)

below <- (Q1 - (0.65) * IQR)
below
above <- (Q3 + (0.65) * IQR)
above

high_tier <- high_tier %>%
  filter(`P/M` >= below & `P/M` <= above) %>%
  select(-`P/M`)

high_tier <- high_tier %>%
  mutate(`p/m²` = (0.52901*Rent)/Area_sqm)

count(high_tier)

high_tier_ln <- high_tier %>%
  mutate_at(vars(Area_sqm, N_rooms, N_bathrooms, N_parking_spaces, 
                 Hosp_1000, Term_1000, Shop_1000, `Green_Area_%`, 
                 `Irregular_settelments_%`, School_Public_1000, 
                 School_Private_1000, Homi_1000,
                 Population, Density, Rent, `p/m²`), log) %>%
  mutate_at(vars(Area_sqm, N_rooms, N_bathrooms, N_parking_spaces, 
                 Hosp_1000, Term_1000, Shop_1000, `Green_Area_%`, 
                 `Irregular_settelments_%`, School_Public_1000, 
                 School_Private_1000, Homi_1000,
                 Population, Density, Rent, `p/m²`),
            ~ifelse(is.infinite(.), 0, .)) %>%
  relocate(Rent, .before = "Area_sqm") %>%
  select(-c(Tier, Neighborhood, Type, Term_1000, Homi_1000,
                 Population, Rent))

high_lm_ln <- lm(`p/m²` ~ ., 
                data = high_tier_ln)

plot(high_lm_ln)
qplot(high_lm_ln$residuals)

shapiro.test(high_lm_ln$residuals) 
jarque.bera.test(high_lm_ln$residuals)

bptest(high_lm_ln)
white_test(high_lm_ln)

durbinWatsonTest(high_lm_ln)

pairs.panels(high_tier_ln)
car::vif(high_lm_ln)

summary(high_lm_ln)

```

### 2.3.2. Addressing the heteroscedasticity of the model using the Newey-West procedure.
```{r echo = TRUE}

coeftest(high_lm_ln, vcov = NeweyWest(high_lm_ln))

```

---

# 3. Endogeneity Tests

* NOTE 3 = According to Fávero (2005, p. 234-235), it is possible to verify whether a series of variables are endogenous or exogenous through the following procedure: taking into account the regression equation.
$$ y_1 = \beta_0 + \beta_1y_2 + \beta_2z_1 + \beta_3z_2 + \mu_1 $$
* where *y_2* is a variable suspected of being endogenous (that is, it may be correlated with the error term *\mu_1*);
* Thus, a validation of the endogeneity hypothesis involves a new regression, where the variable *y_2* becomes the dependent variable:
$$ y_2 = \pi_0 + \pi_1z_1 + \pi_2z_2 + \pi_3z_3 + \pi_4z_4 + v_2 $$
* Thus, *y_2* will not be correlated with *\mu_1* if and only if the error term of the second regression, *v_2*, is not correlated with the error term of the first, *\mu_1*.
* To this end, the error term *v_2* (or *\hat{v}_2*) is included in the original regression.
$$ y_1 = \beta_0 + \beta_1y_2 + \beta_2z_1 + \beta_3z_2 + \delta_1\hat{v}_2 + e_1 $$
* Thus, if *\delta_1 = 0*, then *\mu_1* and *\hat{v}_2* will not be correlated (with validation provided by the t-test, in that if H0 is rejected, then $$ \delta_1 \neq 0 $$ and *y_2* can be considered endogenous).

## 3.1. Low Stratification
```{r eval = FALSE}

# Variable 1 - Density
a <- lm(Density ~ Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = low_tier_ln) 
summary(a)
residuals <- residuals(a)
low_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = low_tier_ln)
summary(b)

# Variable 2 - Area_sqm
a <- lm(Area_sqm ~ Density + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = low_tier_ln) 
summary(a)
residuals <- residuals(a)
low_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = low_tier_ln)
summary(b)

# Variable 3 - N_rooms
a <- lm(N_rooms ~ Density + Area_sqm + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = low_tier_ln) 
summary(a)
residuals <- residuals(a)
low_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = low_tier_ln)
summary(b) 

# Variable 4 - N_bathrooms 
a <- lm(N_bathrooms ~ Density + Area_sqm + N_rooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = low_tier_ln) 
summary(a)
residuals <- residuals(a)
low_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = low_tier_ln)
summary(b) 

# Variable 5 - N_parking_spaces -- VERIFICAR (alterar nível de significância?)
a <- lm(N_parking_spaces ~ Density + Area_sqm + N_rooms + N_bathrooms + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = low_tier_ln) 
summary(a)
residuals <- residuals(a)
low_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = low_tier_ln)
summary(b) 

# Variable 6 - Hosp_1000
a <- lm(Hosp_1000 ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = low_tier_ln) 
summary(a)
residuals <- residuals(a)
low_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = low_tier_ln)
summary(b)

# Variable 7 - Shop_1000
a <- lm(Shop_1000 ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = low_tier_ln) 
summary(a)
residuals <- residuals(a)
low_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = low_tier_ln)
summary(b) 

# Variable 8 - School_Public_1000
a <- lm(School_Public_1000 ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = low_tier_ln) 
summary(a)
residuals <- residuals(a)
low_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = low_tier_ln)
summary(b) 

# Variable 9 - School_Private_1000
a <- lm(School_Private_1000 ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = low_tier_ln) 
summary(a)
residuals <- residuals(a)
low_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = low_tier_ln)
summary(b) 

# Variable 10 - Green_Area_%
a <- lm(`Green_Area_%` ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 
        +`Irregular_settelments_%`,
       data = low_tier_ln) 
summary(a)
residuals <- residuals(a)
low_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = low_tier_ln)
summary(b) 

# Variable 11 - Irregular_settlelments_%
a <- lm(`Irregular_settelments_%` ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 
        +`Green_Area_%`,
       data = low_tier_ln) 
summary(a)
residuals <- residuals(a)
low_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = low_tier_ln)
summary(b) 

```

## 3.1. Medium Stratification
```{r eval = FALSE}

# Variable 1 - Density
a <- lm(Density ~ Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = mid_tier_ln) 
summary(a)
residuals <- residuals(a)
mid_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = mid_tier_ln)
summary(b) 

# Variable 2 - Area_sqm
a <- lm(Area_sqm ~ Density + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = mid_tier_ln) 
summary(a)
residuals <- residuals(a)
mid_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = mid_tier_ln)
summary(b) 

# Variable 3 - N_rooms
a <- lm(N_rooms ~ Density + Area_sqm + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = mid_tier_ln) 
summary(a)
residuals <- residuals(a)
mid_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = mid_tier_ln)
summary(b) 

# Variable 4 - N_bathrooms
a <- lm(N_bathrooms ~ Density + Area_sqm + N_rooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = mid_tier_ln)
summary(a)
residuals <- residuals(a)
mid_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = mid_tier_ln)
summary(b) 

# Variable 5 - N_parking_spaces
a <- lm(N_parking_spaces ~ Density + Area_sqm + N_rooms + N_bathrooms + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = mid_tier_ln)
summary(a)
residuals <- residuals(a)
mid_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = mid_tier_ln)
summary(b) 

# Variable 6 - Hosp_1000
a <- lm(Hosp_1000 ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = mid_tier_ln) 
summary(a)
residuals <- residuals(a)
mid_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = mid_tier_ln)
summary(b)

# Variable 7 - Shop_1000
a <- lm(Shop_1000 ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = mid_tier_ln) 
summary(a)
residuals <- residuals(a)
mid_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = mid_tier_ln)
summary(b)

# Variable 8 - School_Public_1000
a <- lm(School_Public_1000 ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = mid_tier_ln) 
summary(a)
residuals <- residuals(a)
mid_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = mid_tier_ln)
summary(b) 

# Variable 9 - School_Private_1000
a <- lm(School_Private_1000 ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = mid_tier_ln)
summary(a)
residuals <- residuals(a)
mid_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = mid_tier_ln)
summary(b)

# Variable 10 - Green_Area_%
a <- lm(`Green_Area_%` ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 
        +`Irregular_settelments_%`,
       data = mid_tier_ln) 
summary(a)
residuals <- residuals(a)
mid_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = mid_tier_ln)
summary(b)

# Variable 11 - Irregular_settlelments_%
a <- lm(`Irregular_settelments_%` ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 
        +`Green_Area_%`,
       data = mid_tier_ln)
summary(a)
residuals <- residuals(a)
mid_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = mid_tier_ln)
summary(b)

```

## 3.1. High Stratification
```{r eval = FALSE}

# Variable 1 - Density
a <- lm(Density ~ Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = high_tier_ln) 
summary(a)
residuals <- residuals(a)
high_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = high_tier_ln)
summary(b) 

# Variable 2 - Area_sqm
a <- lm(Area_sqm ~ Density + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` +`Irregular_settelments_%`,
       data = high_tier_ln) 
summary(a)
residuals <- residuals(a)
high_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = high_tier_ln)
summary(b)

# Variable 3 - N_rooms
a <- lm(N_rooms ~ Density + Area_sqm + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = high_tier_ln) 
summary(a)
residuals <- residuals(a)
high_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = high_tier_ln)
summary(b) 

# Variable 4 - N_bathrooms
a <- lm(N_bathrooms ~ Density + Area_sqm + N_rooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = high_tier_ln) 
summary(a)
residuals <- residuals(a)
high_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = high_tier_ln)
summary(b)

# Variable 5 - N_parking_spaces
a <- lm(N_parking_spaces ~ Density + Area_sqm + N_rooms + N_bathrooms + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = high_tier_ln) 
summary(a)
residuals <- residuals(a)
high_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = high_tier_ln)
summary(b) 

# Variable 6 - Hosp_1000
a <- lm(Hosp_1000 ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Shop_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = high_tier_ln) 
summary(a)
residuals <- residuals(a)
high_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = high_tier_ln)
summary(b)

# Variable 7 - Shop_1000
a <- lm(Shop_1000 ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + School_Public_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = high_tier_ln) 
summary(a)
residuals <- residuals(a)
high_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = high_tier_ln)
summary(b) 

# Variable 8 - School_Public_1000
a <- lm(School_Public_1000 ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Private_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = high_tier_ln)
summary(a)
residuals <- residuals(a)
high_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = high_tier_ln)
summary(b) 

# Variable 9 - School_Private_1000
a <- lm(School_Private_1000 ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + `Green_Area_%` 
        +`Irregular_settelments_%`,
       data = high_tier_ln) 
summary(a)
residuals <- residuals(a)
high_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = high_tier_ln)
summary(b)

# Variable 10 - Green_Area_%
a <- lm(`Green_Area_%` ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 
        +`Irregular_settelments_%`,
       data = high_tier_ln)
summary(a)
residuals <- residuals(a)
high_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = high_tier_ln)
summary(b)

# Variable 11 - Irregular_settlelments_%
a <- lm(`Irregular_settelments_%` ~ Density + Area_sqm + N_rooms + N_bathrooms + N_parking_spaces + Hosp_1000 + Shop_1000 + School_Public_1000 + School_Private_1000 
        +`Green_Area_%`,
       data = high_tier_ln) 
summary(a)
residuals <- residuals(a)
high_tier_ln$Residuals <- ifelse(is.na(log(residuals)) | is.nan(log(residuals)), 0, log(residuals))

b <- lm(`p/m²` ~ ., 
        data = high_tier_ln)
summary(b)

```

---

# 4. Chow Tests

## 4.1. Low vs. Medium Stratifications
```{r echo = TRUE}

y1 <- log(low_tier$`p/m²`)
x1 <- low_tier %>%
  select(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`) %>%
  mutate_at(vars(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`), log) %>%
  mutate_at(vars(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`),
            ~ifelse(is.infinite(.), 0, .)) %>%
  as.matrix()

y2 <- log(mid_tier$`p/m²`)
x2 <- mid_tier %>%
  select(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`) %>%
  mutate_at(vars(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`), log) %>%
  mutate_at(vars(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`),
            ~ifelse(is.infinite(.), 0, .)) %>%
  as.matrix()

chow.test(y1, x1, y2, x2)

```

## 4.2. Low vs. High Stratifications
```{r echo = TRUE}

y1 <- log(low_tier$`p/m²`)
x1 <- low_tier %>%
  select(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`) %>%
  mutate_at(vars(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`), log) %>%
  mutate_at(vars(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`),
            ~ifelse(is.infinite(.), 0, .)) %>%
  as.matrix()

y2 <- log(high_tier$`p/m²`)
x2 <- high_tier %>%
  select(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`) %>%
  mutate_at(vars(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`), log) %>%
  mutate_at(vars(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`),
            ~ifelse(is.infinite(.), 0, .)) %>%
  as.matrix()

chow.test(y1, x1, y2, x2)

```

## 4.3. Medium vs. High Stratifications
```{r echo = TRUE}

y1 <- log(mid_tier$`p/m²`)
x1 <- mid_tier %>%
  select(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`) %>%
  mutate_at(vars(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`), log) %>%
  mutate_at(vars(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`),
            ~ifelse(is.infinite(.), 0, .)) %>%
  as.matrix()

y2 <- log(high_tier$`p/m²`)
x2 <- high_tier %>%
  select(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`) %>%
  mutate_at(vars(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`), log) %>%
  mutate_at(vars(Density, Area_sqm, N_rooms, N_bathrooms, N_parking_spaces,
         Hosp_1000, Shop_1000, School_Public_1000, School_Private_1000,
         `Green_Area_%`, `Irregular_settelments_%`),
            ~ifelse(is.infinite(.), 0, .)) %>%
  as.matrix()

chow.test(y1, x1, y2, x2)

```
